---
title: "Metadata for Retained Catch Data: Raw Estimates"
subtitle: "Retained catch data covering IOTC species and associated bycatch, reported before being broken down into species- and gear-specific components"
author: "Author: [IOTC Secretariat](mailto:IOTC-Secretariat@fao.org)"
output:
  html_document2:
    number_sections: FALSE
    toc: yes
    toc_float:
      collapsed: FALSE
      smooth_scroll: FALSE
---

```{r general_options, echo = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  size = 'small',

  tab.cap.pre = "Table ",
  tab.cap.sep = ". ",
  tab.cap.style ='Table Caption',

  fig.cap.style = "Caption label",
  fig.cap.pre = "Fig. ",
  fig.cap.sep = ". ",

  fig.width   = 8,
  fig.height  = 4.5
)

knit_hooks$set(
  inline = function(x) {
    prettyNum(x, big.mark = "")
  }
)
```

## Abstract

This dataset corresponds to the latest version of the raw estimates of annual catches in live-weight equivalent for the all species for which catches are submitted to the Secretariat, aggregated by year, IOTC statistical area and fishing fleet. Data are reported by calendar year and extend back to the 1950s, when industrial longlining started in the Indian Ocean.

The data originate from the IOTC Contracting Parties and Cooperating Non-Contracting Parties ([CPCs]((https://iotc.org/about-iotc/structure-commission) )) as per the IOTC data requirements (Resolution [15/02](https://www.iotc.org/cmm/resolution-1502-mandatory-statistical-reporting-requirements-iotc-contracting-parties-and)). They are submitted annually, mostly using IOTC Form [1RC](https://data.iotc.org/reference/latest/forms/#Form_1RC), and curated by the Secretariat for dissemination prior to IOTC Working Parties and other scientific data users.

Data were consolidated to include catches for non-IOTC members, generally from the FAO Global Capture Production Database. In some cases, the Secretariat may re-estimate the species or gear composition for strata affected by known data collection or reporting issues. These re-estimations are made in agreement with the IOTC Scientific Committee and may be revised in future updates.

## Global Attributes

- **Title**: Reported and consolidated retained catches for IOTC and associated bycatch species by year, IOTC statistical area and fishing fleet, `r paste0(min(RC_RAW$YEAR), "-", max(RC_RAW$YEAR))`
- **Summary**: This dataset contains annual retained catches in live-weight equivalent for all IOTC species and associated bycatch species taken in tuna and tuna-like fisheries of the Indian Ocean. Data are primarily derived from catches reported to the IOTC by Contracting Parties and Cooperating Non-Contracting Parties (CPCs), and are complemented through consolidation to improve coverage, including catches from non-IOTC Members where available. Catches are aggregated by calendar year, IOTC statistical area and fishing fleet, and are not systematically disaggregated by fishing gear or species for certain aggregated reporting categories
- **Context of development**: Management and scientific assessment of tuna and tuna-like species under the mandate of the Indian Ocean Tuna Commission (IOTC)
- **Data origin**: Retained catch data collected on land and at sea by national institutions and the fishing industry
- **Lineage**: Catch data submitted by IOTC Contracting Parties and Cooperating Non-Contracting Parties (CPCs), and subsequently reviewed, complemented and consolidated by the IOTC Secretariat
- **Keywords**: IOTC species; retained catch; tuna and tuna-like species; Indian Ocean; fisheries statistics
- **Type**: Tabular dataset
- **Format**: CSV
- **Size**: 
    + `r prettyNum(RC_RAW_FILES_SIZE["csvFileSizeKB"], big.mark = ",")` KB for original dataset
    + `r prettyNum(RC_RAW_FILES_SIZE["zipFileSizeKB"], big.mark = ",")` KB for compressed dataset
- **Structures**: `r prettyNum(nrow(RC_RAW), big.mark = ",")` rows x `r prettyNum(ncol(RC_RAW), big.mark = ",")` columns
- **Geographic description**: Indian Ocean fishing areas, as defined by the [IOTC statistical areas](https://data.iotc.org/reference/latest/domain/admin/#IOTC_Main_Areas)
- **Update frequency**: Irregular; updated following data submissions, revisions and consolidations
- **Metadata production date**: `r format(Sys.time(), '%d %B %Y')`
- **Source**: [Indian Ocean Tuna Commission (IOTC)](https://www.iotc.org/)
- **Data curator**: IOTC Secretariat
- **Contact**: [IOTC-Statistics@fao.org](mailto:IOTC-Statistics@fao.org)
- **Associated rights**: Public-domain data; source acknowledgement required

## Data Fields

```{r RCFieldsDefinitions, fig.cap = ""}
datatable(FIELDS_RC_DATA_TABLE, escape = FALSE, rownames = FALSE, options = list(dom = 't', pageLength = nrow(FIELDS_RC_DATA_TABLE)))
```
